---
title: "March Airbnb Listings"
author: "Yu Zhou"
date: "2023-07-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load library

```{r}
library(tidyverse)
library(ggplot2)
library(sf)
library(tmap)
library(gridExtra)
library(e1071)
library(spatstat)
library(geojsonio)
library(gstat)
library(raster)
library(spdep)
library(osrm)
library(osmdata)
library(ggmap) # Google's Terms of Service: <https://mapsplatform.google.com>
# ℹ Please cite ggmap if you use it! Use `citation("ggmap")` for details.
library(RColorBrewer)
library(fixest)
library(car)
library(tmaptools)
library(OpenStreetMap)
library(sp)
library(gstat)
library(tmap)
library(classInt)
library(viridis)
library(viridisLite)
library(ggsn)
library(ggspatial)
library(prettymapr)
library(sp)
library(spdep)
library(osrm)
```

# Import data

This dataset is based on the 2023-03-14 London extract from Inside Airbnb. The original set includes AirBnb property listings with characteristics and price, and this is extended to additional variables based on each property's location.

```{r}
# listing <- read.csv("data/listings.csv") # 75241 obs. / 75 variables

neighbourhoods <- st_read("data/borough/neighbourhoods.geojson")
borough_sf <- neighbourhoods %>% st_transform(st_crs(listings_sf))
# st_write(neighbourhoods_sf, "neighbourhoods.shp")
```


```{r}
listings <- nn %>% 
  mutate(ID = row_number()) %>% 
  dplyr::select(ID, Price, lnPrice, latitude, longitude, neighbourhood_cleansed,
              accommodates, bathrooms, bedrooms, amenities_num,
              number_of_reviews_l30d, review_scores_location, review_scores_value,
              availability_60, instant_bookable, 
              host_is_superhost, host_identity_verified,
              calculated_host_listings_count)
  
# 31,656 × 18
```


## Convert data

```{r}
# The Coordinate Reference System (CRS)
listings_sf <- listings %>% 
  st_as_sf(coords = c("longitude", "latitude")) %>%  # create sf
  st_set_crs(4326) %>%
  st_transform(27700) 


Price_sf <- listings %>% 
  dplyr::select(ID, longitude, latitude, Price, lnPrice, neighbourhood_cleansed) %>% 
  st_as_sf(coords = c("longitude", "latitude")) %>%  # create sf
  st_set_crs(4326) %>%
  st_transform(27700) 


Price <- listings %>% 
  dplyr::select(ID, longitude, latitude, Price, lnPrice, neighbourhood_cleansed)
# write.csv(Price, file = "price_kepler.csv")
# write.csv(listings, file = "listings.csv")
```

# POI

## specify London area

```{r}
London_area <- opq(bbox = "London")
# "51.2867601,-0.5103751,51.6918741,0.3340155"


# remove all fields with missing values
not_all_na <- function(x) any(!is.na(x))
```

## get all the POI number from London

```{r}
# Define the function
get_feature <- function(key, value) {
  
  query <- London_area %>% add_osm_feature(key = key, value = value) 
  osm_feature <- osmdata_sf(query)
  
  # Function to process each component of osm_feature
  process_feature <- function(feature) {
    if (!is.null(feature)) {
        feature %>% filter(sf::st_is_valid(.)) %>% 
        dplyr::select(where(not_all_na)) %>% 
        st_centroid()
      
    } else {
      NULL
    }
  }
  
  osm_points <- process_feature(osm_feature$osm_points)
  osm_lines <- process_feature(osm_feature$osm_lines)
  osm_polygons <- process_feature(osm_feature$osm_polygons)
  osm_multilines <- process_feature(osm_feature$osm_multilines)
  osm_multipolygons <- process_feature(osm_feature$osm_multipolygons)
  
  results <- bind_rows(osm_points, osm_lines, osm_polygons, 
                       osm_multilines, osm_multipolygons)
  
  return(results)
}

```

```{r}
# apply the function

# london_bar <- get_feature(key = 'amenity', value = 'bar') # 3116
# london_pub <- get_feature(key = 'amenity', value = 'pub') # 20020
# london_barpub <- get_feature(key = 'amenity', value = c('bar', 'pub')) # 23092 
# london_cafe <- get_feature(key = 'amenity', value = 'cafe') # 16437
london_restaurant <- get_feature(key = 'amenity', value = 'restaurant') # 24540
london_mall <- get_feature(key = 'shop', value = 'mall') # 3861
london_convenience <- get_feature(key = 'shop', value = 'convenience') # 14654

london_bus_stop <- get_feature(key = 'highway', value = 'bus_stop') # 24139
london_subway_entrance <- get_feature(key = 'railway', value = 'subway_entrance') # 560
london_railway_station <- get_feature(key = 'public_transport', value = 'station') # 1935

london_attraction <- get_feature(key = 'tourism', value = 'attraction') # 7637
london_museum <- get_feature(key = 'tourism', value = 'museum') # 2259
london_theatre <- get_feature(key = 'amenity', value = 'theatre') # 2738
# london_gallery <- get_feature(key = 'tourism', value = 'gallery') # 952
```


## data to QGIS
```{r}
london_restaurant_poi <- 
  st_transform(london_restaurant, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_restaurant_poi, "london_restaurant_poi.shp")

london_mall_poi <- 
  st_transform(london_mall, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_mall_poi, "london_mall_poi.shp")

london_convenience_poi <- 
  st_transform(london_convenience, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_convenience_poi, "london_convenience_poi.shp")



london_bus_stop_poi <- 
  st_transform(london_bus_stop, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_bus_stop_poi, "london_bus_stop_poi.shp")

london_subway_entrance_poi <- 
  st_transform(london_subway_entrance, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_subway_entrance_poi, "london_subway_entrance_poi.shp")

london_railway_station_poi <- 
  st_transform(london_railway_station, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_railway_station_poi, "london_railway_station_poi.shp")




london_attraction_poi <- 
  st_transform(london_attraction, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_attraction_poi, "london_attraction_poi.shp")

london_museum_poi <- 
  st_transform(london_museum, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_museum_poi, "london_museum_poi.shp")

london_theatre_poi <- 
  st_transform(london_theatre, st_crs(listings_sf)) %>% 
  dplyr::select(osm_id, geometry)
st_write(london_theatre_poi, "london_theatre_poi.shp")
```



## Distance

```{r}
# Define the function
calculate_distance_to_poi <- function(price_sf, poi) {
  # Transform CRS
  poi <- st_transform(poi, st_crs(price_sf))
  
  # Find nearest points and calculate distance
  distances <- st_distance(price_sf, poi)
  
  # Get the minimum distance for each listing point
  min_distances <- apply(distances, 1, min) / 1000 # distances in units of CRS
  
  
  return(as.data.frame(min_distances))
}



mall_dist <- calculate_distance_to_poi(Price_sf, mall_sf)
subway_entrance_dist <- calculate_distance_to_poi(Price_sf, subway_entrance_sf)
railway_station_dist <- calculate_distance_to_poi(Price_sf, railway_station_sf)
attraction_dist <- calculate_distance_to_poi(Price_sf, attraction_sf)
museum_dist <- calculate_distance_to_poi(Price_sf, museum_sf)
theatre_dist <- calculate_distance_to_poi(Price_sf, theatre_sf)
# gallery_dist_km <- calculate_distance_to_poi(Price_sf, london_gallery)
```


# POIs sf
```{r}
restaurant_sf <- read_sf("data/restaurant_sf.shp") # 25996
mall_sf <- read_sf("data/mall_sf.shp") # 3113
convenience_sf <- read_sf("data/convenience_sf.shp") # 15270

bus_stop_sf <- read_sf("data/bus_stop_sf.shp") # 19939
subway_entrance_sf <- read_sf("data/subway_entrance_sf.shp") # 552
railway_station_sf <- read_sf("data/railway_station_sf.shp") # 1740

attraction_sf <- read_sf("data/attraction_sf.shp") # 7094
museum_sf <- read_sf("data/museum_sf.shp") # 2194
theatre_sf <- read_sf("data/theatre_sf.shp") # 2653
```


## POI plot
```{r}
p1 <- ggplot() +
  geom_sf(data = restaurant_sf, color = "indianred3", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Restaurant") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
  


p2 <- ggplot() +
  geom_sf(data = mall_sf, color = "cornflowerblue", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Shopping Mall") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


p3 <- ggplot() +
  geom_sf(data = convenience_sf, color = "darkgoldenrod2", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Convenience Shop") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


p4 <- ggplot() +
  geom_sf(data = bus_stop_sf, color = "mediumpurple1", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Bus Stop") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))



p5 <- ggplot() +
  geom_sf(data = subway_entrance_sf, color = "palevioletred3", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Subway Entrance") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


p6 <- ggplot() +
  geom_sf(data = railway_station_sf, color = "springgreen3", 
          size = 0.6) +
   geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Railway Station") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))



p7 <- ggplot() +
  geom_sf(data = attraction_sf, color = "darkgreen", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Attraction") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


p8 <- ggplot() +
  geom_sf(data = museum_sf, color = "sienna2", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE) +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Museum") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


p9 <- ggplot() +
  geom_sf(data = theatre_sf, color = "royalblue3", 
          size = 0.6) +
  geom_sf(data = borough_sf, fill = NA, color = "black") +
  theme_void() + 
  ggsn::scalebar(data = borough_sf, dist = 5, dist_unit = "km",
                 location = "bottomright", transform = FALSE, model = "WGS84",
                 st.size = 3.2, border.size = 0.3, st.bottom = FALSE)  +
  ggsn::north(data = borough_sf, location = "topright", scale = 0.13, symbol = 1) +
  labs(title = "Theatre") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


# Arrange and save the plots
# ggsave("my_plot.png", grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3), width = 15, height = 15)


grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow = 3)
```


## number of POI within 500/1000 meters
```{r}
restaurant_1km <- read_sf("data/restaurant_1km.shp") %>% as.data.frame() %>% 
  dplyr::select(ID, NUMPOINTS) %>% 
  dplyr::rename(restaurant_1km = NUMPOINTS)


convenience_500m <- read_sf("data/convenience_500m.shp") %>% as.data.frame() %>% 
  dplyr::select(ID, convenienc) %>% 
  dplyr::rename(convenience_500m = convenienc)


bus_stop_500m <- read_sf("data/bus_stop_500m.shp") %>% as.data.frame() %>% 
  dplyr::select(ID, NUMPOINTS) %>% 
  dplyr::rename(bus_stop_500m = NUMPOINTS)

```

## Merge all the data
```{r}
listings_poi <- listings %>%
  
  # restaurant_1km
  left_join(restaurant_1km, join_by(ID == ID)) %>% 
   # mall_dist
  cbind(mall_dist) %>% 
  dplyr::rename(mall_dist= min_distances) %>% 
  # convenience_500m
  left_join(convenience_500m, join_by(ID == ID)) %>% 
  
  # bus_stop_500m
  left_join(bus_stop_500m, join_by(ID == ID)) %>% 
  # subway_entrance_dist
  cbind(subway_entrance_dist) %>% 
  dplyr::rename(subway_entrance_dist = min_distances) %>% 
  # railway_station_dist
  cbind(railway_station_dist) %>% 
  dplyr::rename(railway_station_dist = min_distances) %>% 
  
  # attraction_dist
  cbind(attraction_dist) %>% 
  dplyr::rename(attraction_dist = min_distances) %>% 
  # museum_dist
  cbind(museum_dist) %>% 
  dplyr::rename(museum_dist = min_distances) %>%
  # theatre_dist
  cbind(theatre_dist) %>% 
  dplyr::rename(theatre_dist = min_distances)


sum(is.na(listings_poi))

# write.csv(listings_poi, "Total_Listings.csv")

```


# Intervel Distribution Plot of All Independent Variables
```{r}
pp1 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = accommodates), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$accommodates), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Accommodate", x = NULL, y = NULL)


pp2 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = bathrooms), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$bathrooms), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Bathroom", x = NULL, y = NULL)

pp3 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = bedrooms), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$bedrooms), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Bedroom", x = NULL, y = NULL)


pp4 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = amenities_num), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$amenities_num), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Number of Amenities", x = NULL, y = NULL)


pp5 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = number_of_reviews_l30d), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$number_of_reviews_l30d), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Number of Reviews in Last 30 Days", x = NULL, y = NULL)


pp6 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = review_scores_location), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$review_scores_location), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Review Scores on Location", x = NULL, y = NULL)


pp7 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = review_scores_value), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$review_scores_value), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Review Scores on Value", x = NULL, y = NULL)


pp8 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = availability_60), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$availability_60), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Availability Day in Next 60 Days", x = NULL, y = NULL)

Listings$instant_bookable <- as.numeric(Listings$instant_bookable)
Listings$host_is_superhost <- as.numeric(Listings$host_is_superhost)
Listings$host_identity_verified <- as.numeric(Listings$host_identity_verified)
  
pp9 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = instant_bookable), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$instant_bookable), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Instant Bookable", x = NULL, y = NULL)


pp10 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = host_is_superhost), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$host_is_superhost), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Host is Superhost", x = NULL, y = NULL)


pp11 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = host_identity_verified), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$host_identity_verified), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Host Identity is Verified", x = NULL, y = NULL)



pp12 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = calculated_host_listings_count), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$calculated_host_listings_count), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Calculated Host Listings Count", x = NULL, y = NULL)



p_1 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = restaurant_1km), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$restaurant_1km), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Restaurant", x = NULL, y = NULL)


p_2 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = mall_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$mall_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Shopping Mall", x = NULL, y = NULL)


p_3 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = convenience_500m), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$convenience_500m), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Convenience Shop", x = NULL, y = NULL)


p_4 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = bus_stop_500m), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$bus_stop_500m), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Bus Stop", x = NULL, y = NULL)


p_5 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = subway_entrance_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$subway_entrance_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Subway Entrance", x = NULL, y = NULL)


p_6 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = railway_station_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$railway_station_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Railway Station", x = NULL, y = NULL)


p_7 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = attraction_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$attraction_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Attraction", x = NULL, y = NULL)

p_8 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = museum_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$museum_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Museum", x = NULL, y = NULL)

p_9 <- listings_poi %>% 
  ggplot() +
  theme_minimal() +
  geom_histogram(mapping=aes(x = theatre_dist), 
                 color = "grey40", alpha = 1, bins = 50, fill="skyblue1") +
  geom_vline(xintercept = mean(Listings$theatre_dist), color = "indianred1") +
  theme(axis.ticks.y = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10)) +
  labs(title = "Theatre", x = NULL, y = NULL)

grid.arrange(pp1, pp2, pp3, pp4, pp5, pp6, pp7, pp8, pp9, pp10, pp11, pp12,
             p_1, p_2, p_3, p_4, p_5, p_6, p_7, p_8, p_9,
             ncol = 3)


ggsave("pp.png", 
       grid.arrange(pp1, pp2, pp3, pp4, pp5, pp6, pp7, pp8, pp9, pp10, pp11, pp12,
                    p_1, p_2, p_3, p_4, p_5, p_6, p_7, p_8, p_9,
                    ncol = 3),
       width = 9, height = 12)
```



# Dependent Variable - Listings Price / lnPrice

### Density

```{r}
skewness(Price$Price) # 3.526329
skewness(Price$lnPrice) # 0.6360177
# A skewness value > 0 means that there is more weight in the left tail of the distribution (positive skew)
#  stabilize variance using logarithmic transformations


p1 <- Price %>% ggplot() +
  geom_histogram(mapping=aes(x = Price, y=..density..), 
                 color = "grey40", alpha = 1, bins=40, fill="cornsilk") + 
  geom_density(mapping = aes(x = Price), color="black") +
  geom_vline(xintercept = mean(Price$Price), color = "indianred1") +
  labs(title = "Density Distribution of Listing Price", x = "Price (£)", y = "Density") +
   theme_classic() +
   theme (axis.ticks.y = element_blank(),
          legend.position = "none",
          axis.ticks.x = element_blank(),
          plot.title = element_text(face = "bold", hjust = 0.5, size = 10))


p2 <- Price %>% ggplot() +
  geom_histogram(mapping=aes(x = lnPrice, y=..density..), 
                 color = "grey40",alpha = 1, bins=40, fill="cornsilk") +
  geom_density(mapping = aes(x = lnPrice), color="black") +
  geom_vline(xintercept = mean(Price$lnPrice), color = "indianred1") +
  labs(title = "Density Distribution of Listing lnPrice", x = "lnPrice (£)", y = "Density") +  theme_classic() +
   theme (axis.ticks.y = element_blank(),
          legend.position = "none",
          axis.ticks.x = element_blank(),
          plot.title = element_text(face = "bold", hjust = 0.5, size = 10))

grid.arrange(p1, p2, ncol = 1)
```

### Boxplot by borough

```{r}
# Calculate median price for each borough
borough_medians <- with(listings, tapply(Price, neighbourhood_cleansed, median, na.rm = TRUE))

test <- listings
# Reorder factor levels of 'neighbourhood_cleansed' based on median price
test$neighbourhood_cleansed <- with(listings, reorder(neighbourhood_cleansed, Price, FUN = median))

# Plot
borough1 <- ggplot(data = test, 
       aes(x = Price, y = neighbourhood_cleansed, 
           color = neighbourhood_cleansed)) + 
   geom_boxplot() + 
   theme_classic() +
   theme(legend.position="none",
         plot.title = element_text(hjust = 0.5, size = 21, face = "bold"), 
         axis.title.x = element_text(size = 18, face = "bold"), 
         axis.title.y = element_text(size = 18, face = "bold"),
         axis.text = element_text(size = 15, face = "bold")) +
 labs(x = "Price (£)", y = "Borough")


 # Save the plot with a height of 10 inches
ggsave("borough1.png", plot = borough1, height = 12, width = 12, units = "in")
```



